### 2014-03-20 table_grammatical_paths.tex

subst:subst{\textunderscore}{\textunderscore}KOORD{\textunderscore}up{\textunderscore}{\textunderscore}PUTFYLL{\textunderscore}up{\textunderscore}{\textunderscore}ATR{\textunderscore}up & 3 & NP-internal \\

>>>>

subst:subst{\textunderscore}{\textunderscore}KOORD{\textunderscore}up{\textunderscore}{\textunderscore}PUTFYLL{\textunderscore}up{\textunderscore}{\textunderscore}ATR{\textunderscore}up & 1 & NP-internal \\
